Well Hello There!

### 2024-05-28 index.qmd
Update

## My Hello to You \~

@@

![](docs/src/images/brochure.png)

>>>>

## My Hello to You \~~

@@

<div style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;">
  <iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;"
    src="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">
  </iframe>
</div>

<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> Virtual Memory Garden </a>
